---
title: "Ziqiu Practice"
author: "Ziqiu"
date: "June 7, 2016"
output: html_document
---

Create regular expressions for the patterns below:

Match any of the following punctuation characters in the ASCII table: !“#$%&’()+,
```{r}
"[[:punct:]]"
```

Create one regular expression to match all common misspellings of calendar (see https://en.wikipedia.org/wiki/Wikipedia:Lists_of_common_misspellings/C)
```{r}
#calander (calendar, calender, colander)
"c[a|e|o]l[e|a]nder"
```

Create one regular expression to match any character except line breaks.
```{r}
".*\N"
```

You need to validate a ZIP code (U.S. postal code), allowing both the five-digit and nine-digit (called ZIP+4) formats. The regex should match 02115 and 02115-5515, but not 2115, 2115-5515, 21155515,021155515, etc.
```{r}
"[0-9]{5}(\-[0-9]{4})?"
```

You need to validate a legit any password for your website. Passwords have the following complexity requirements: Length between 8 and 32 characters, ASCII visible and space characters only, One or more uppercase letters, One or more lowercase letters, One or more special characters (ASCII punctuation)
```{r}
if(grepl("[a-z]+",x)&grepl("[A-Z]+",x)& grepl("[0-9]+",x)&grepl("[[:punct:]]",x))
  return(TRUE)
```

Load the file M08_tweets.csv (it is online at ‘http://nikbearbrown.com/YouTube/MachineLearning/M08/M08_tweets.csv’)

Complete the following:
Extract a list of the top 9 users (e.g. @NikBearBrown)
Extract a list of the top 9 hashtags (e.g. #Bear)
```{r}
require(stringr)
require(tm)
require(wordcloud)
tw<-read.csv("http://nikbearbrown.com/YouTube/MachineLearning/M08/M08_tweets.csv",header = FALSE)

str1.corpus <- Corpus(DataframeSource(data.frame(tw)))
#inspect(str1.corpus)
str1.clean<-tm_map(str1.corpus, stripWhitespace)
str1.clean.lc <- tm_map(str1.clean, content_transformer(tolower))
str1.clean <- tm_map(str1.clean.lc, removeWords, stopwords("english"))
str1.tdm <- TermDocumentMatrix(str1.clean, control = list(minWordLength = 1))
str1.tdm
#inspect(str1.tdm)
list1<-findFreqTerms(str1.tdm, lowfreq=220)
grep("@.+",list1,value = TRUE)
list2<-findFreqTerms(str1.tdm, lowfreq=520)
grep("#.+",list2,value = TRUE)
```
From the frequency, we can see the top9 users are "@darkestdungeon", "@freakingtrue", "@hoodieallen", "@infoduniabahasa", "@juegodetronostm", "@nickidaily", "@nickiworldnews", "@sincerelytumblr", "@youtube".
Top9 hashtags are:"#android"     "#bigdata"     "#game"        "#gamedev"     "#gameinsight" "#indiedev" "#indiegame"   "#ipad"        "#ipadgames,"  "#kca"         "#unity3d" 

Find the top 5 most positve tweets
Find the top 5 most negative tweets
Create a world cloud of 100 related tweets
Which tweets could be classified as game development?
```{r}
tw<-as.matrix(tw)
# remove retweet entities
tw <- gsub("(RT|via)((?:\\b\\W*@\\w+)+)", "", tw)
# remove at people
tw <- gsub("@\\w+", "", tw)
# remove punctuation
tw <- gsub("[[:punct:]]", "", tw)
# remove numbers
tw <- gsub("[[:digit:]]", "", tw)
# remove html links
tw <- gsub("http\\w+", "", tw)
# remove unnecessary spaces
tw <- gsub("[ \t]{2,}", "", tw)
tw <- gsub("^\\s+|\\s+$", "", tw)
# classify emotion
tw
require(qdap)
ps<-polarity(tw)
data<-as.data.frame(ps$all)
negData<-data[order(data[,3]),]
negData[1:5,]
#The top five negative tweets are:
#line 22294 Pathetic shitty ass fucking joke of a fucking team get bent fuck this game is off u guys r a fucking joke
#line 45076 Pathetic shitty ass fucking joke of a fucking team get bent fuck this game is off u guys r a fucking joke
#line 13606 FUCKING STUPID ITALIAN CUNTS HOPE THEY ALL CHOKE ON THEIR PIZZA AFTER THE GAME DIE DIE DIE
#line 36388 FUCKING STUPID ITALIAN CUNTS HOPE THEY ALL CHOKE ON THEIR PIZZA AFTER THE GAME DIE DIE DIE
#line 50854  killed guard so hard game crashed Overkill
posData<-data[order(-data[,3]),]
head(posData)
#so the postive five are:
#line 4389 Great game great job guys Improving our name We won
#line 4669 Great game great job guys Improving our name We won
#line 27171 Great game great job guys Improving our name We won
#line 75032 Valiant HeartsThe Great Wars is an exceptionally good game Great story telling with history psplus ValiantHearts
#line 66389 Great Great Great matches team yesterday thats what im talking abut everyone brought their a game even myand
```

```{r}
set.seed(333)
tdms <- removeSparseTerms(str1.tdm, 0.999)
v <- sort(rowSums(m), decreasing=TRUE)
myNames <- names(v)
d <- data.frame(word=myNames, freq=v)
wordcloud(d$word, d$freq, min.freq=100,max.words = 100)
```
